Jug: Software for Reproducible Computation

### 2011-11-21 paper.tex
TXT More about development, philosophy, &c

\subsection{Task Based Architecture}

@@

As the reader can appreciate, this is identical to a traditional Python script,
except for the \code{@TaskGenerator} decorators.

@@

@@

Jug has been available in the Python Package Index\footnote{The Python Package
Index, PyPI, is accessible at \url{http://pypi.python.org}.} since May~2009
and has been downloaded over 6000~times (some of these downloads may, of
course, represent upgrades, and users which downloaded it from some other
source will not be counted).% FIXME: Check download number. At 5713 8/31/2011
\section{Methods}
\section{Example}
\section{Discussion}
\end{document}

>>>>

By allowing caching of results, where the caching depends explicitly on the
input parameters of that computation. Any change in the parameters immediately
triggers a recomputation of all dependendent results. The basic model is
similar to the one of the venerable Unix tool Make~\citep{}, which has been
used before for implementing reproducible research pipelines~\citep{}.

However, unlike make, jug is written in Python and tasks can consist of any
Python function and its arguments. A jugfile (the file which specifies which
tasks need to be run---named by analogy to the makefiles of make) is a simple
Python script with some added notations (we will see just how little changes
need to be made from a conventional Python script).

\section{Jug}
\subsection{Task Based Architecture}

@@

As the reader can appreciate, this is identical to a traditional Python script,
except for the \code{@TaskGenerator} decorators. With a few limitations (which
unfortunately can give rise to complex error messages), scripts can be written
as if they were sequential Python scripts.

@@

\section{Methods}
\section{Example}
\section{Development of Jug}
Jug is available under the MIT software license, which grants the user right to
use, copy, and modify the code almost at will. It is developed using the git
version control tool, with the project being hosted on the github
platform.\footnote{The jug project is available at
\url{https://www.github.com/luispedro/jug}.} An open mailing-list provides
support and reported bugs are generally fixed within hours.

@@

Jug has been available in the Python Package Index\footnote{The Python Package
Index, PyPI, is accessible at \url{http://pypi.python.org}.} since May~2009
and has been downloaded over 6000~times (some of these downloads may, of
course, represent upgrades, and users which downloaded it from some other
source will not be counted).% FIXME: Check download number. At 5713 8/31/2011

\section{Discussion}
Unlike most previous tools for reproducible research, jug focuses on the
development of the computation as much as its communication (in fact, when it
comes to communication other tools might be better targetted as they combine
written exposition with computer code). While it still possible to make errors
(for example, by changing the code but neglecting to invalidate the results),
jug improves the pipeline development experience and makes the programming
researcher more productive.

In the last few years, I have not undertaken any computational research project
without the use of jug to manage my computations. The tool has become an
indispensible part of my toolkit.

\end{document}
